Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-02-13 paperIEEE.tex
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@128 db7c848b-7755-4df2-b763-8796797afa52

\begin{figure*}[ht]\center
    \includegraphics[height=.17\textwidth]{images/benchmark_eVolve}
    \includegraphics[height=.17\textwidth]{images/benchmark_eqPly2}
    \includegraphics[height=.17\textwidth]{images/spikes512}
    \includegraphics[height=.17\textwidth]{images/beechnut}
  \caption{\label{fBenchmarks}Benchmark data: Flower alley with 30 volume models
  of $1024^3$ unsigned bytes (1\,GB) each (left); David alley with 30 statues of
  56\,M triangles (988\,MB) each (middle); Volumes used for object distribution
  benchmarks (right): spike frequencies of a three million neuron electrical
  simulation at 512x437x240 unsigned byte (51\,MB) and an MicroCT scan of a
  beechnut at 1024x1024x1546 unsigned short (3\,GB) resolution}
\end{figure*}

>>>>

\begin{figure*}[ht]\center
    \includegraphics[height=.17\textwidth]{images/benchmark_eVolve}
    \includegraphics[height=.17\textwidth]{images/benchmark_eqPly2}
    \includegraphics[height=.17\textwidth]{images/spikes512}
    \includegraphics[height=.17\textwidth]{images/beechnut}
  \caption{\label{fBenchmarks}Benchmark data: Flower alley with 30 volume models
  of $1024^3$ unsigned bytes (1\,GB) each (left); David alley with 30 statues of
  56\,M triangles (988\,MB) each (middle); Volumes used for object distribution
  benchmarks (right): spike frequencies of a three million neuron electrical
  simulation at $512\times437\times240$ unsigned byte (51\,MB) and an MicroCT scan of a
  beechnut at $1024\times1024\times1546$ unsigned short (3\,GB) resolution}
\end{figure*}
